The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-11 rockerverse.Rmd
Update rockerverse.Rmd

>>>>

**\pkg{googleCloudRunner}** is an interface with [Google Cloud Platform](https://cloud.google.com/) container related services, with tools to make it easier for R users to interact with them for common use cases.  It includes deployment functions for creating R APIs using the Docker based [Cloud Run](https://cloud.run) service; create long running batch jobs calling any Docker image including Rocker via [Cloud Build](https://cloud.google.com/cloud-build/) and schedule services using [Cloud Scheduler](https://cloud.google.com/scheduler/).
